Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-25 paper/paper.tex
Added choice of parameters_r to earlier paragraph

The parameter values $\mu_s$ and $\sigma_s$ are obtained by fitting the
distribution of $GoldSim$ values in the training set (see Fig.
\ref{fig:Histograms}). For example, in the $N \geq 80$ dataset we have $\mu_s =
0.27$ and $\sigma_s = 0.25$. The choice of $\mu_r$ and $\sigma_r$ is less clear.
Some insight can be gained, however, by examining the prior distribution of
ratings for our datasets, which are shown in Fig. \ref{fig:RatingDist}.

@@

We observe that while the data of Fig. \ref{fig:RatingDist} clearly do not
conform precisely to a multivariate Gaussian distribution, this approximation is
not an unreasonable one. In passing, we remark on the faint clusters that flank
the central cluster in the figures. We understand these to be artifacts of the
bias subtraction. Moreover, a more sophisticated Rating-based model could
account for these by considering a $P(\vec{R} | Y)$ that is a mixture of
Gaussians. Motivated partly by these density plots and partly by estimator
performance against the training set, we choose $\mu_r = 0.25$ and $\sigma_r =
0.3$ when estimating $TrueSimRand$.

>>>>

The parameter values $\mu_s$ and $\sigma_s$ are obtained by fitting the
distribution of $GoldSim$ values in the training set (see Fig.
\ref{fig:Histograms}). For example, in the $N \geq 80$ dataset we have $\mu_s =
0.27$ and $\sigma_s = 0.25$. The choice of $\mu_r$ and $\sigma_r$ is less clear.
Some insight can be gained by examining the prior distribution of ratings for 
our datasets, which are shown in Fig. \ref{fig:RatingDist}. From there, we
experiment with different values of these parameters to minimize the resulting
error over the training set. We find $\mu_r = 0.25$ and $\sigma_r = 0.3$ to be
good parameters and use them when estimating $TrueSimRand$.

@@

We observe that while the data of Fig. \ref{fig:RatingDist} clearly do not
conform precisely to a multivariate Gaussian distribution, this approximation is
not an unreasonable one. In passing, we remark on the faint clusters that flank
the central cluster in the figures. We understand these to be artifacts of the
bias subtraction. Moreover, a more sophisticated Rating-based model could
account for these by considering a $P(\vec{R} | Y)$ that is a mixture of
Gaussians.
